Solutions to Integer Programming from Quantum Annealing

### 2020-05-09 paper/main.tex
fix some summations and other things (marked in blue)

Formally, ILP is defined as the optimization of a linear function
\begin{align}
f(x) = &\min\limits_{x}(c_i x_i),\\
\textrm{subject to} \quad & A_{aj}x_i +b_a \leq 0 \\
& x_i \geq 0,\\
& x_i \in \mathbb{Z}
\end{align}
where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations. The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
\begin{align}
f(x) = &\min(c_i x_i),\\
\textrm{subject to} \quad & A_{a i}x_i + s_a + b_a = 0,\\
& s_a \geq 0,\\
& s_a \in \mathbb{Z},\\
& x_i \geq 0,\\
& x_i \in \mathbb{Z}.
\end{align}

Since quantum annealing solves the QUBO problem, we extend the proposed algorithm to solve integer quadratic optimization problems such that
\begin{align}
f(x) = \min\limits_{x}(x_i d_{ij} x_j + c_i x_i)
\end{align}
without the introduction of auxiliary qubits.

@@

Intuitively, we want the system to explore a larger state space to increase the probability for the system to reach the final ground state. That is, we want the system to have ergodicity in order to avoid MBL. On the other hand, decoherence in the hardware leads to the loss of quantum information. It is therefore desirable to minimize the effect of relaxation. The interplay between these two competing effects can be observed by looking at the time-dependent probability of reaching the final ground state, and the mutual information. The mutual information is defined as $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition $A$ and partition $B$ of the total system. $S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$.

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian in Eq.~(\ref{eq:tdhamiltonian}). $[,]$ denotes the Lie bracket. $L_j$ are the Lindblad operators for decoherence. $\{, \}$ denotes the anti-commutator. In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$. For simplicity we assume all qubits having the same relaxation time. The initial condition is the Gibbs canonical ensemble
\begin{equation}
\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} .
\end{equation}
The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $. Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.

>>>>

Formally, ILP is defined as the optimization of a linear function
{\color{blue}
\begin{align}
f(x) = &\min\limits_{x}(\sum_i c_i x_i),\\
\textrm{subject to} \quad & \sum_i A_{ai}x_i +b_a \leq 0 \\
& x_i \geq 0,\\
& x_i \in \mathbb{Z}
\end{align}
}
where $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations. The inequality constraints can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
{\color{blue}
\begin{align}
f(x) = &\min(\sum_i c_i x_i),\\
\textrm{subject to} \quad & \sum_i A_{a i}x_i + s_a + b_a = 0,\\
& s_a \geq 0,\\
& s_a \in \mathbb{Z},\\
& x_i \geq 0,\\
& x_i \in \mathbb{Z}.
\end{align}
}
Since quantum annealing solves the QUBO problem, we extend the proposed algorithm to solve integer quadratic optimization problems such that
{\color{blue}
\begin{align}
f(x) = \min\limits_{x}(\sum_{ij} x_i d_{ij} x_j + \sum_i c_i x_i)
\end{align}
}
without the introduction of auxiliary qubits.

@@

Intuitively, we want the system to explore a larger state space to increase the probability for the system to reach the final ground state. That is, we want the system to have ergodicity in order to avoid MBL. On the other hand, decoherence in the hardware leads to the loss of quantum information. It is therefore desirable to minimize the effect of relaxation. The interplay between these two competing effects can be observed by looking at the time-dependent probability of reaching the final ground state, and the mutual information. The mutual information is defined as $I(A:B)=S(\rho_A)+S(\rho_B)-S(\rho_{A,B})$, which quantifies how many bits of quantum information is communicated between partition $A$ and partition $B$ of the total system. $S(\rho)=-\mbox{Tr}\rho \log_2 \rho$ is the von Neumann entropy of density matrix $\rho$. {\color{blue} $\rho_{A,B}$ is the density matrix for the total system. $\rho_{A}=\mbox{Tr}_{B} (\rho_{A,B})$ is the reduced density matrix for the subsystem A.}

@@

To solve for time evolution dynamics of quantum annealing including thermal and the decoherence effects, we solve for the master equation in Lindblad form
\begin{align}
\partial_t \rho (t) =  \frac{-i}{\hbar} [H(t) , \rho(t)] + \sum_j (2L_j \rho(t) L_j^\dagger - \{ L^\dagger_j L_j, \rho(t) \}) ,
\end{align}
where $\rho (t)$ is the density matrix at time $t$. $H(t)$ is the time-dependent Hamiltonian 
\begin{align}
\label{eq:annealH}
 H_{anneal}(t)&  =  - \sum_i  A_i(t)\sigma^x_i & \notag \\ 
 +&  \sum_{i>j} \sqrt{B_{i}(t)B_{j}(t)} J_{ij} \sigma^z_i \sigma^z_j +\sum_i B_{i}(t) h_i \sigma^z_i  ,&
\end{align}
where $A_i(t)$ and $B_{i}(t)$ are site-dependent annealing schedule functions. The site dependency takes into account of the annealing offset. $[,]$ denotes the Lie bracket. $L_j$ are the Lindblad operators for decoherence. $\{, \}$ denotes the anti-commutator. In this study we only include a minimal model for decoherence, i.e., the amplitude damping for non-interacting qubits. The Lindblad operator is $L_j=\sqrt{\gamma} \sigma^{+}_j$ for $h_j>0$ and $L_j=\sqrt{\gamma} \sigma^{-}_j$ for $h_j<0$, where $\gamma = 1/T_1$ is the decoherence rate for relaxation time $T_1$. For simplicity we assume all qubits having the same relaxation time. The initial condition is the Gibbs canonical ensemble
\begin{equation}
\rho (0) =  \frac{e^{-\beta H(0)}}{\mbox{Tr}[e^{-\beta H(0)}]} ,
\end{equation}
where $\beta$ is the inverse temperature.
The probability to get the ground state at measurement is
\begin{align}
P =  \mbox{Tr} \{  \rho (t) \pi_{\mbox{gnd}} \}  ,
\end{align}
where the projection operator onto the degenerated ground states subspace is defined as $\pi_{\mbox{gnd}}=\sum_{i\in G} |\mbox{gnd}_i\rangle \langle \mbox{gnd}_i| $. Here $\{ | \mbox{gnd}_i \rangle | i \in G \}$ forms an orthonormal basis for the degenerated ground states subspace, i.e., $\langle \mbox{gnd}_j | \mbox{gnd}_i \rangle = \delta_{ij}$.
